---
title: "Article Template"
output:
  word_document: default
  pdf_document: default
  html_document:
    keep_md: true
geometry: margin= 1.0in
font-size: 11pt
header-includes: 
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{colortbl}
editor_options: 
  chunk_output_type: console
# knit: (function(input, ...) {
#     rmarkdown::render(
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
library(knitr)
library(kableExtra)
library(tidyverse)
library(gt)
library(gtsummary)
library(webshot2)
```

# **`r rmarkdown::metadata$title`** 

\vspace{10mm}

**Running Title:**

\vspace{10mm}

Author Name 1 ${^\dagger}$ , Author Name 2, ...

${\dagger}$ To whom correspondance should be addressed

\vspace{10mm}
 
Department of ...  
... University  
Address  

\vspace{10mm}

**Observation Format**

\newpage

## Abstract (... words)
Here goes an **Abstract** text.

## Importance (... words)
Here goes an **Importance** text.

* Importance I 
  * Importance-I-a
  * Importance-I-b
* Importance II
* Importance III

\newpage

## Introduction
Here goes an **Introduction** text.

\newpage

## Results
Here goes an **Results** text.

example results from {gtsummary} package named `trial`.

```{r}
trial %>% head() %>% kbl()
```


### Results-I
Here goes an **Results-I** text.

### Results-II
Here goes an **Results-II** text.

\newpage

## Conclusions
Here goes an **Conclusions** text.

* Conclusions-I
  * Conclusions-I-a
  * Conclusions-I-b
* Conclusions-II
* Conclusions-III

\newpage

## Materials & Methods
Here goes an **Materials & Methods** text.


\newpage

## Tables
Here  **Tables** text.

\vspace{2mm}
`table_1` using the {gtsummary} package

```{r table_1}
trial %>% 
  select(trt, age, grade) %>%
  tbl_summary(by = trt) %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 2)) %>%
  add_overall() %>%
  add_n() %>%
  modify_header(label ~ "Variable") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "Treatment Received") %>%
  modify_footnote(
    all_stat_cols() ~ "Median (IQR) or Frequency (%)") %>% 
  as_gt() %>% 
  as_latex()
```

**Table 1: with gtsummary package**

\newpage

`table_2` using the {gt} package

\vspace{2mm}

```{r table_2}
trial %>%
  dplyr::select(trt, age, grade) %>%
  dplyr::slice(1:5) %>%
  gt() %>%
  tab_header(
    title = md("`trial` Data from {gtsummary} package"),
    subtitle = md("`trial` is an {gtsummary} dataset")
  ) %>%
  as_latex()
```

**Table 2: with {gt} package (needs manipulation in gt)**

\vspace{2mm}

\newpage

`table_3` using the {gtsummary} & {kableExtra} package 
{kableExtra} add caption of table within code give number of table by code.

\arrayrulecolor{white}

```{r table_3}
trial %>% 
  select(trt, age, grade) %>%
  tbl_summary(by = trt) %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 2)) %>%
  add_overall() %>%
  add_n() %>%
  modify_header(label ~ "Variable", text_interpret = "md") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "Treatment Received") %>%
  modify_footnote(
    all_stat_cols() ~ "Median (IQR) or Frequency (%)") %>% 
  as_kable_extra(caption = "Table 3 with {gtsummary} and {kableExtra} packages") %>% 
  kable_styling(full_width = FALSE,
                latex_options = "HOLD_position", 
                font_size = 10)
```

\vspace{2mm}

\newpage

`table_4` using the {gtsummary} & {kableExtra} package

\vspace{2mm}

```{r table_4}
trial %>% 
  select(trt, age, grade) %>% 
  tbl_summary(by = trt) %>%
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 2)) %>%
  add_overall() %>%
  add_n() %>%
  modify_header(label ~ "**Variable**") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Treatment Received**") %>%
  modify_footnote(all_stat_cols() ~ "Median (IQR) or Frequency (%)") %>%
  modify_caption("**Patient Characteristics**") %>%
  bold_labels() %>% 
  as_kable_extra() %>% 
  kable_styling(full_width = FALSE,
                latex_options = "HOLD_position", 
                font_size = 10, stripe_color = white)
```

\newpage

## Figures

Here goes a **Figures** text.

\vspace{2mm}

\includegraphics{figures/trial_plot.pdf}

**Figure 1. trial plot with ggplot2**

\newpage

```{r cars-plot, fig.cap = "Sample figure for trial data with ggplot2"}
trial_plot = trial %>%
  select(1,2) %>% 
  ggplot(aes(x = trt, y = age)) +
  geom_boxplot()+
  theme_bw()
ggsave(plot = trial_plot,filename = "figures/trial_plot.tiff", width = 5, height = 5)
ggsave(plot = trial_plot,filename = "figures/trial_plot.pdf", width = 5, height = 5)
```

```{r figure-1, fig.cap = "Sample figure for trial data with ggplot2"}
knitr::include_graphics("figures/trial_plot.pdf")
```

\newpage

## Acknowledgements
Here goes an **Acknowledgements** text.

\newpage

## References

